---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# checkRtrack

<!-- badges: start -->
<!-- badges: end -->

R package to define track widths. It is created for the course "Introduction to Programming with R" and for my HiWi. 
For now, you can define the lowest points along your track to then define the outer limits of the tracks and then visualize your progress. 
The main idea is, that you have digitized (animal)-tracks and a (high resolution) Digital Surface Model (DSM). 
The animals stamping out the grassland could make the width of the path visible with the DSM. The width is defined as the steepest point on each side of the path. With parameters you can adjust your calculations of the width and then always visualize it to check out what is going on. To understand the parameters, please see section 'What are these parameters for?'.

The goal is later, to create the mean width for each track segment. 


Here is a workflow example that could help with understanding how it works:


## Installation

Let us first install the package:

``` r
# install.packages("devtools")
devtools::install_github("geoniesun/checkRtrack")

   library(ggplot2)
   library(sf)
   library(terra)
   library(qgisprocess)
   library(dplyr)
   library(ggnewscale)
   library(tidyterra)
   library(colorspace)
   library(ggspatial)
```

Next step would be to load the data - the digitized tracks and the DSM:


```r
#load tracks 
tracks <- read_tracks("your/path/tracks.gpkg")

#load dsm
dsm <- read_dsm("your/path/dsm.tif")

```
For now, it's always best to start with generating the minimumpoints. (Check the setting of the parameters under section 'What are these parameters for?). You can also export the GeoPackage and work on it in QGIS or similar:

```r
# create a variable 'mini' to have it ready for the visualization later
mini <- checkMin(dsm, tracks, export = FALSE, dist_cross = 1, profile_length = 1, dist_cross_points = 0.05, st_dev = 0.06)

```
Let's have a first look on our minimumpoints. As the entire dataset with all points would be too messy for a quick Map, you will always get a random spot on your tracks that you can have a look on. So just run the line as many times as you want, to have a look on different areas.

```r
#creating a random zoom plot of the minimumpoints
checkMap(dsm, tracks, points = mini, export = FALSE)

```
Now let's see for the sides. You can go immediately for both sides with 'checkSides()' or look on each one with 'checkRight()' or 'checkLeft()'. For now we go with both:

```r
#generate side extend of the path
sides <- checkSides(dsm, tracks, export = FALSE, dist_cross = 1, profile_length = 1, dist_cross_points = 0.05)
```
Let's check again the map:

```r
#plot random map of minimum and side points
checkMap(dsm, tracks, points = mini, morepoints = sides, export = FALSE)

```

## What are these parameters for?

We have three parameters that we can adjust. This depends on your size of tracks that you want to look at.

![alt text](https://github.com/geoniesun/checkRtrack/[main]/images/paramters.png?raw=true)


## Exemplary Usage



```{r example}
#library(checkRtrack)
## basic example code
```

## Roadmap
- [ ]  Fix bug: when fade_scr not included, plot looks wrong
- [ ]  Visualize the crossprofiles from the side. To see if there is actually a path
- [ ]  Take out the fade score as necessary column
- [ ]  Set more filter that determine a path
- [ ]  Create more options to modify the users definition of the "path end" (for now its the steepest slope point)

